Data Management \\ and LSST Special Programs

### 2017-11-10 ms.tex
minor typos

\begin{enumerate}[resume,topsep=-10pt,after=\vspace{10pt},label= \textbf{Action \Roman*}] \item \label{reconfig-1} The purpose of this ticket is to investigate the DM staffing needs required to reconfigure pipelines for Special Programs, test and validate them, and then run and verify their products -- during commissioning and into operations. Questions to be answered include, e.g., product ownership of the reconfigured pipelines and test data products, and how do we set goals and deadlines for this? \end{enumerate}

@@

\begin{enumerate}[resume,topsep=-10pt,after=\vspace{10pt},label= \textbf{Action \Roman*}] \item \label{DMSR-0} RFC: We propose that the DMSR include a high-level specification (probably in Section 1.6) that the data from Special Programs will be included in the products of the wide-fast-deep main survey only when it is (a) possible and (b) beneficial to the primary science objectives of those products. It should also be updated to reflect the fact that DM will reconfigure its own pipelines ``wherever possible", process the Special Programs data, verify the unique data products, and make them publicly available. This would be a flow-down requirement from a similar new one added to the LSR (LSE-29).  \end{enumerate}

>>>>

\begin{enumerate}[resume,topsep=-10pt,after=\vspace{10pt},label= \textbf{Action \Roman*}] \item \label{reconfig-1} The purpose of this ticket is to clarify the DM staffing needs required to reconfigure pipelines for Special Programs, test and validate them, and then run and verify their products -- during commissioning and into operations. Questions to be answered include, e.g., product ownership of the reconfigured pipelines and test data products, and how do we set goals and deadlines for this? \end{enumerate}

@@

\begin{enumerate}[resume,topsep=-10pt,after=\vspace{10pt},label= \textbf{Action \Roman*}] \item \label{DMSR-0} RFC (LSE-61): We propose that the DMSR include a high-level specification (probably in Section 1.6) that the data from Special Programs will be included in the products of the wide-fast-deep main survey only when it is (a) possible and (b) beneficial to the primary science objectives of those products. It should also be updated to reflect the fact that DM will reconfigure its own pipelines ``wherever possible", process the Special Programs data, verify the unique data products, and make them publicly available. This would be a flow-down requirement from a similar new one added to the LSR (LSE-29).  \end{enumerate}
